---
title: "Financial data analysis"
author: "Leslie"
format: html
---
```{r}
#| message: false
library(vroom) # or readr
library(ggplot2)
library(dplyr)
library(tidyr)
library(here)
```

## Data loading
```{r}
#| message: false
clients <- vroom(here("data","client.csv"))
accounts <- vroom(here("data","account.csv"))
disp <- vroom(here("data","disp.csv"))
```

## Joining data
A collection of joining functions of the form `*_join`. 

### Inner join
```{r}
da <- inner_join(accounts, disp)
```
join has been done using account_id variable / there's only one column in commom = account_id

```{r}
cda <- inner_join(clients, da)
```
```{r}
cda <- inner_join(clients, da, by = join_by("client_id"), suffix = c("home", "bank"))
```
More options to keep both district_id variables

### Home district vs Bank district
```{r}
home_diff_bank <- cda |> filter(district_idhome != district_idbank) |> nrow()
```
at first, those people were excluded because they have different district home and bank. 
We observe that `r home_diff_bank`clients have a bank in another distric as the one they live in.

```{r}
cda |> group_by(account_id) |> distinct(district_idhome) |> 
  summarise(N=n()) |> filter(N>1)
```
filter operates at a level of a single row but we want to compare many persons so many rows so we group_by over account id.


